
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{\protect\numberline{}{\bf Bibliograf\'ia}}
\rhead[\fancyplain{}{\bf Bibliograf\'ia}]
      {\fancyplain{}{\bfseries\thepage}}

\bibitem{complex} Andreescu T., Andrica D., \textit{Complex numbers from A to
 $\dots$ Z}, Birkh\"auser, 2005.

\bibitem{challenges} Andreescu T., Gelca R., \textit{Mathematical Olympiad 
Challenges}, Birkh\"auser, 2000.

\bibitem{treasures} Andreescu T., Enescu B., \textit{Mathematical Olympiad 
Treasures}, Birkh\"auser, 2006.

\bibitem{barbeau} Barbeau E. J., 
\textit{Polynomials},  Springer-Verlag, 1989.

\bibitem{bulajichgomez}  Bulajich Manfrino R., G'omez Ortega J.A.,
\textit{Geometr'ia}, Cuadernos de Olimpiadas, Instituto de Matem'aticas de la 
Universidad Nacional Aut'onoma de M'exico, Sociedad Matem'atica Mexicana, 2012.

\bibitem{bulajich1}  Bulajich Manfrino R., G'omez Ortega J.A., Valdez Delgado 
R., \textit{Desigualdades}, Cuadernos de Olimpiadas, Instituto de Matem'aticas 
de la Universidad Nacional Aut'onoma de M'exico, Sociedad Matem'atica Mexicana,
2010.

\bibitem{bulajich} Bulajich Manfrino R., G'omez Ortega J.A., Valdez Delgado R., 
\textit{Inequalities: A Mathematical Olympiad Approach }, Birkh\"auser, 2009.


\bibitem{cardenas}  C'ardenas H., Lluis E., Raggi F., Tom'as F. 
\textit{'Algebra Superior}, Editorial Trillas, 1973.


\bibitem{IMOcompendium} Djuki\'c D., Jankovi\'c V., Mati\'c I., Petrovi\'c N.,
\textit{The IMO Compendium}, Springer, 2006. 

\bibitem{engel} Engel A., \textit{Problem-Solving Strategies}, Springer,
1998.

\bibitem{fine} Fine B., Resenberger G., \textit{The Fundamental Theorem of
 Algebra}, Springer, 1997.
 
\bibitem{goldberg}  Goldberg S.,
\textit{Introduction to Differece Equations}, Dover Publications, 1958.

\bibitem{casillas}  G'omez Ortega J.A., Valdez Delgado R., V'azquez Padilla,
\textit{Principio de las Casillas}, Cuadernos de Olimpiadas, 
Instituto de Matem'aticas de la Universidad Nacional Aut'onoma de 
M'exico, Sociedad Matem'atica Mexicana, 2014.

\bibitem{honsberger} Honsberger R.,
\textit{Ingenuity in Mathematics}, vol. 23 in New Mathematical Library 
series,  1962.

%\bibitem{marsden} Marsden J.E., Tromba A.J., \textit{Vector Calculus}, W.H. Freeman and %Company, New York, Third Edition, 1988.

\bibitem{niven} Niven I., Montgomery H. \& Zuckerman H.,
\textit{An Introduction to the Theory of Numbers}, Wiley,  5 edition,  1991.


\bibitem{remmert} Remmert R., \textit{Theory  of Complex Functions}, Springer,
 1999.
  
\bibitem{rudin} Rudin W., \textit{Principles of Mathematical Analysis},
McGraw-Hill, 1976.

\bibitem{miniatures} Savchev S., Andreescu T., \textit{Mathematical Miniatures},
The Mathematical Association of America, 2003.

\bibitem{small} Small C.G., 
\textit{Functional Equations and How to Solve Them}, Springer, 2007.

\bibitem{pablo} Sober'on P., 
\textit{Combinatoria para Olimpiadas Internacionales}, Cuadernos de la Olimpiada, Instituto de Matem'aticas de la Universidad Aut'onoma de M'exico, Sociedad Matem'atica Mexicana,  2010.

\bibitem{spivak} Spivak M., 
\textit{Calculus}, Editorial Revert'e, 3era edici\'on, 2012.

\bibitem{serge} Tabachnikov, S. (Editor), {\it Kvant Selecta: Algebra and 
Analysis II}, American Mathematical Society, 1999.

\bibitem{functional} Venkatachala B. J., \textit{Functional Equations. A
Problem Solving Approach}, Prism Books Pvt Ltd, 2002.

\end{thebibliography}
